Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2016-10-02 article/article_for_submission.tex
changes L, boxplot legend dashed line instead of line
Small changes in comments for PCA example in section 5.2 (article for submission)

Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$. The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$. The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
\centering
\includegraphics[width=0.45\textwidth]{Images/boxplots.pdf}
\label{boxplots.gfunc}
\end{figure}
As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower estimation errors for these four inputs. The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4} \sim 10^{-5}$).
\bigskip

@@

As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged estimation errors and total number of evaluations for Variant $A.a$ and Variant $A.b$.
\begin{table}[!ht]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.a$.}
\centering
\begin{tabular}{ccccccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
 $x_1$ & $0.6529$ &  $0.0004$ & $0$ & $0.7396$ & $0.0003$ & $0.$ \\ \hline
 $x_2$ & $0.1791$ &  $0.0006$ & $0$ & $0.2659$ & $0.0004$ & $0$ \\ \hline
 $x_3$ & $0.0370$ &  $0.0058$ & $0.71$ & $0.0764$ & $0.0012$ & $0.02$ \\ \hline
 $x_4$ & $0.0133$ &  $0.0022$ & $0.12$ & $0.0343$ & $0.0020$ & $0.07$ \\ \hline
 $x_5$ & $0.0015$ &  $0.0024$ & $0.11$ & $0.0062$ & $0.0014$ & $0$ \\ \hline
 $x_6$ & $0.0015$ & $0.0021$ & $0.06$  & $0.0062$ & $0.0010$ & $0.03$ \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} & & &\\ \hline 
\end{tabular}
\label{res.bratley.Aa}
\end{table}
\begin{table}[!ht]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.b$.}
\centering
\begin{tabular}{ccccccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ & $r_{\delta_{\overline{S}_u}}$ \\ \hline
 $x_1$ & $0.6529$ &  $0.0004$ & $0$ & $0.7396$ & $0.0003$ & $0$ \\ \hline
 $x_2$ & $0.1791$ &  $0.0006$ & $0$ & $0.2659$ & $0.0005$ & $0$ \\ \hline
 $x_3$ & $0.0370$ &  $0.0019$ & $0.04$ & $0.0764$ & $0.0013$ & $0.01$ \\ \hline
 $x_4$ & $0.0133$ &  $0.0016$ & $0.01$ & $0.0343$ & $0.0017$ & $0.02$ \\ \hline
 $x_5$ & $0.0015$ &  $0.0003$ & $0$ & $0.0062$ & $0.0015$ & $0.04$ \\ \hline
 $x_6$ & $0.0015$ &  $0.0004$ & $0$  & $0.0062$ & $0.0011$ & $0$ \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $68 \ 045$} & & &\\ \hline 
\end{tabular}
\label{res.bratley.Ab}
\end{table}
Variant $A.b$ gives lower estimation errors and fewer failure rates than Variant $A.a$ on the four small first-indices $\underline{S}_3,\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''. The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $4\%$ for Variant $A.b$. Furthermore, Variant $A.b$ requires less evaluations than Variant $A.a$. The boxplots represented in Figure \ref{boxplots.bratley} emphasize the latter observations.
\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$. The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
\centering
\includegraphics[width=0.45\textwidth]{Images/boxplots_bis.pdf}
\label{boxplots.bratley}
\end{figure}

@@

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with PCA decomposition.}
\centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$  \\ \hline
 $x_1$ & $0.9800$ \\ \hline
 $x_2$ & $0.0037$ \\ \hline
 $x_3$ & $0.0028$ \\ \hline
 $x_4$ & $0.0029$ \\ \hline
 $x_5$ & $0.0017$ \\ \hline
 $x_6$ & $0.0029$ \\ \hline \hline
\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
\end{tabular}
\label{res.AsianPCA.B}
\end{table}
Variant $A.b$ performs equally well as Variant $A.a$ in terms of average total number of evaluations while most probably giving better estimates for the small first-order indices. Once 	again, variant $B$ shows an improvement on the total number of evaluations with the drawback of slightly overestimating the small first-order indices.

>>>>

Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$. The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$. The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
\centering
\includegraphics[width=0.45\textwidth]{Images/boxplots.pdf}
\label{boxplots.gfunc}
\end{figure}
As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower estimation errors for these four inputs. The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4} \sim 10^{-5}$).
\bigskip

@@

As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged estimation errors and total number of evaluations for Variant $A.a$ and Variant $A.b$.
\begin{table}[!ht]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.a$.}
\centering
\begin{tabular}{ccccccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
 $x_1$ & $0.6529$ &  $0.0004$ & $0$ & $0.7396$ & $0.0003$ & $0.$ \\ \hline
 $x_2$ & $0.1791$ &  $0.0006$ & $0$ & $0.2659$ & $0.0004$ & $0$ \\ \hline
 $x_3$ & $0.0370$ &  $0.0058$ & $0.71$ & $0.0764$ & $0.0012$ & $0.02$ \\ \hline
 $x_4$ & $0.0133$ &  $0.0022$ & $0.12$ & $0.0343$ & $0.0020$ & $0.07$ \\ \hline
 $x_5$ & $0.0015$ &  $0.0024$ & $0.11$ & $0.0062$ & $0.0014$ & $0$ \\ \hline
 $x_6$ & $0.0015$ & $0.0021$ & $0.06$  & $0.0062$ & $0.0010$ & $0.03$ \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} & & &\\ \hline 
\end{tabular}
\label{res.bratley.Aa}
\end{table}
\begin{table}[!ht]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.b$.}
\centering
\begin{tabular}{ccccccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ & $r_{\delta_{\overline{S}_u}}$ \\ \hline
 $x_1$ & $0.6529$ &  $0.0004$ & $0$ & $0.7396$ & $0.0003$ & $0$ \\ \hline
 $x_2$ & $0.1791$ &  $0.0006$ & $0$ & $0.2659$ & $0.0005$ & $0$ \\ \hline
 $x_3$ & $0.0370$ &  $0.0019$ & $0.04$ & $0.0764$ & $0.0013$ & $0.01$ \\ \hline
 $x_4$ & $0.0133$ &  $0.0016$ & $0.01$ & $0.0343$ & $0.0017$ & $0.02$ \\ \hline
 $x_5$ & $0.0015$ &  $0.0003$ & $0$ & $0.0062$ & $0.0015$ & $0.04$ \\ \hline
 $x_6$ & $0.0015$ &  $0.0004$ & $0$  & $0.0062$ & $0.0011$ & $0$ \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $68 \ 045$} & & &\\ \hline 
\end{tabular}
\label{res.bratley.Ab}
\end{table}
Variant $A.b$ gives lower estimation errors and fewer failure rates than Variant $A.a$ on the four small first-indices $\underline{S}_3,\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''. The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $4\%$ for Variant $A.b$. Furthermore, Variant $A.b$ requires less evaluations than Variant $A.a$. The boxplots represented in Figure \ref{boxplots.bratley} emphasize the latter observations.
\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$. The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
\centering
\includegraphics[width=0.45\textwidth]{Images/boxplots_bis.pdf}
\label{boxplots.bratley}
\end{figure}

@@

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with PCA decomposition.}
\centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$  \\ \hline
 $x_1$ & $0.9800$ \\ \hline
 $x_2$ & $0.0037$ \\ \hline
 $x_3$ & $0.0028$ \\ \hline
 $x_4$ & $0.0029$ \\ \hline
 $x_5$ & $0.0017$ \\ \hline
 $x_6$ & $0.0029$ \\ \hline \hline
\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
\end{tabular}
\label{res.AsianPCA.B}
\end{table}
Variant $A.a$ performs as well as Variant $A.b$ in terms of average total number of evaluations. However, Variant $A.a$ is most probably giving worse estimates for the small first-order indices. Table \ref{res.AsianPCA.Aa} shows that averaged $\widehat{\underline{S}}_4$ is greater than $\widehat{\overline{S}}_4$, $\widehat{\underline{S}}_5$ greater than $\widehat{\overline{S}}_5$, and $\widehat{\underline{S}}_6$ greater than $\widehat{\overline{S}}_6$, which is inconsistent with the property ${\underline{S}}_u\leq{\overline{S}}_u$. Once again, variant $B$ shows an improvement on the total number of evaluations with the drawback of slightly overestimating the small first-order indices.
